Domain Specific Languages and Code Synthesis

### 2014-03-14 paper.tex
Edits to Section 2

An Embedded DSL (EDSL) is a language inside a language.
Haskell~\cite{Haskell98Book}, the premier pure functional programming language, is a great host for EDSLs
because of flexible overloading, a powerful type system, and lazy semantics facilitating this.
In this section, we give a terse
introduction to Haskell, 
sufficient to make this article self-contained. This section was
is an extended version the Haskell primer given by the author in~\cite{?}.

@@

On top of these basic types, Haskell has two syntactical forms for expressing
compound types.
First, pairs, triples and larger structures can be written using tuple syntax,
comma separated types inside parenthesis.
So \verb|(Int,Bool)| is structure with both an \verb|Int| and a \verb|Bool| component.
Second, lists have a syntactical shortcut, using square brackets.
So \verb|[Int]| is a list of \verb|Int|.

>>>>

An Embedded DSL (EDSL) is a language inside a language.
Haskell~\cite{Haskell98Book}, the premier pure functional programming language, is a great host for EDSLs
because of flexible overloading, a powerful type system, and lazy semantics.
In this section, we give a terse
introduction to Haskell, 
sufficient to make this article self-contained. This section
is an extended version of the Haskell primer given by the author in~\cite{?}.

@@

On top of these basic types, Haskell has two syntactic forms for expressing
compound types.
First, pairs, triples and larger structures can be written using tuple syntax,
comma separated types inside parenthesis.
So \verb|(Int,Bool)| is structure with both an \verb|Int| and a \verb|Bool| component.
Second, lists have a syntactic shortcut, using square brackets.
So \verb|[Int]| is a list of \verb|Int|.
